MCC Models

### 2019-08-05 papers/full_paper/SI_appendix.Rmd

>>>>

Now, to compute $P_{S_1}(u_3|r_3)$, we need the informativity for $r_3$ given the other utterance with the same label. We need

$$
\begin{aligned}
& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
\end{aligned}
$$
and

$$
\begin{aligned}
&P_{L_0}(r_3|u_1) =  P_{L_0}(r_3, \mathcal{L}_1|u_1) + P_{L_0}(r_1, \mathcal{L}_2|u_1) = 0+0=0 \\
\end{aligned}
$$
as well as

$$
\begin{aligned}
&Informativity(u_1; r_3) = log(0) = -\infty \\
\end{aligned}
$$

to get

$$
P_{S_1}(u_3|r_3) = \frac{exp(2.24 \times -1.43)}{exp(2.24 \times -1.43)+exp(2.24 \times -\infty)}=1
$$
Thus, the probability that the speaker will chose $u_3$ to refer to $r_3$ is 1. We can now turn to equation 1 to get the probability with which the pragmatic listener ($L_1$) think that the Speaker ($S_1$) is referring to $r_3$ when producing utterance $u_3$.

MANUEL: THE ABOVE HAS TO BE TRUE, AT LEAST THIS IS THE VALUE WE GET OUT OF THE WEBPPL MODEL.

To get the probability with which the pragmatic listener $L_1$ think that the $S_1$ is referring to $r_3$ when producing utterance
